Gut-resident microorganisms and their genes are associated with cognition and neuroanatomy in children

### 2023-08-26 manuscript/main.tex

\begin{table}[!h]
    \centering
    \begin{tabular}{|r|r|r|r|r|}
      \hline\hline
      \textbf{Group} & \textbf{Subgroup} & \textbf{All} & \textbf{Under 6 months} & \textbf{Over 18 months} \\\hline
      N subjects &  & 361 & 74 & 257 \\  \hline
    \multirow{3}{*}{Samples} & 1 & 262 (72.6\%) & 74 (100.0\%) & 203 (79.0\%) \\ \cline{2-5}
         & 2 & 72 (19.9\%) & 0 (0.0\%) & 46 (17.9\%) \\ \cline{2-5}
         & \textgreater 2 & 27 (7.5\%) & 0 (0.0\%) & 8 (3.1\%) \\ \hline
    \multirow{3}{*}{Age (months)} & min & 2.76 & 2.76 & 18.03 \\ \cline{2-5}
         & max & 119.3 & 6.0 & 119.3 \\ \cline{2-5}
         & median & 25.79 & 3.66 & 45.92 \\ \hline
    \multirow{2}{*}{Sex} & F & 163 (45.2\%) & 37 (50.0\%) & 114 (44.4\%) \\   \cline{2-5}
                         & M & 198 (54.8\%) & 37 (50.0\%) & 143 (55.6\%) \\  \hline
    \multirow{6}{*}{Race} & White & 252 (69.8\%) & 42 (56.8\%) & 191 (74.3\%) \\   \cline{2-5}
        & Black & 40 (11.1\%) & 16 (21.6\%) & 21 (8.2\%) \\ \cline{2-5}
        & Indiginous & 1 (0.3\%) & 0 (0.0\%) & 1 (0.4\%) \\ \cline{2-5}
        & Asian & 7 (1.9\%) & 1 (1.4\%) & 6 (2.3\%) \\ \cline{2-5}
        & Mixed & 48 (13.3\%) & 12 (16.2\%) & 29 (11.3\%) \\ \cline{2-5}
        & Other & 2 (0.6\%) & 1 (1.4\%) & 2 (0.8\%) \\ \hline
    \multirow{6}{*}{Maternal Ed.} & Junior high school & 1 (0.3\%) & 0 (0.0\%) & 1 (0.4\%) \\   \cline{2-5}
        & Some high school & 6 (1.7\%) & 3 (4.1\%) & 4 (1.6\%) \\ \cline{2-5}
        & High school grad & 37 (10.2\%) & 13 (17.6\%) & 16 (6.2\%) \\ \cline{2-5}
        & Some college & 95 (26.3\%) & 25 (33.8\%) & 57 (22.2\%) \\ \cline{2-5}
        & College grad & 90 (24.9\%) & 17 (23.0\%) & 69 (26.8\%) \\ \cline{2-5}
        & Grad/professional school & 123 (34.1\%) & 15 (20.3\%) & 104 (40.5\%) \\\hline\hline
    \end{tabular}
    \caption{\label{tab:demo}Subject demographics of the ECHO RESONANCE cohort.}
\end{table}

>>>>

\begin{table}[!h]
    \centering
    \begin{tabular}{|r|r|r|r|r|}
      \hline\hline
      \textbf{Group} & \textbf{Subgroup} & \textbf{All} & \textbf{Under 6 months} & \textbf{Over 18 months} \\\hline
      N subjects &  & 381 & 149 & 328 \\  \hline
    \multirow{3}{*}{Samples} & 1 & 77 (20.2\%) & 125 (83.9\%) & 92 (28.0\%) \\ \cline{2-5}
         & 2 & 65 (17.1\%) & 20 (13.4\%) & 80 (24.4\%) \\ \cline{2-5}
         & \textgreater 2 & 239 (62.7\%) & 4 (2.7\%) & 156 (47.6\%) \\ \hline
    \multirow{3}{*}{Age (months)} & min & 2.89 & 2.89 & 18.03 \\ \cline{2-5}
         & max & 119.53 & 5.95 & 119.53 \\ \cline{2-5}
         & median & 25.85 & 3.64 & 41.59 \\ \hline
    \multirow{2}{*}{Sex} & F & 172 (45.1\%) & 42 (51.2\%) & 122 (44.0\%) \\   \cline{2-5}
                         & M & 209 (54.9\%) & 40 (48.8\%) & 155 (56.0\%) \\  \hline
    \multirow{6}{*}{Race} & White & 265 (69.6\%) & 48 (58.5\%) & 201 (72.6\%) \\   \cline{2-5}
        & Black & 40 (10.5\%) & 15 (18.3\%) & 21 (7.6\%) \\ \cline{2-5}
        & Indigenous & 1 (0.3\%) & 0 (0.0\%) & 1 (0.4\%) \\ \cline{2-5}
        & Asian & 8 (2.1\%) & 2 (2.4\%) & 7 (2.5\%) \\ \cline{2-5}
        & Mixed & 54 (14.2\%) & 14 (17.1\%) & 38 (13.7\%) \\ \cline{2-5}
        & Other & 3 (0.8\%) & 1 (1.2\%) & 3 (1.1\%) \\ \hline
    \multirow{6}{*}{Maternal Ed.} & Junior high school & 2 (0.5\%) & 0 (0.0\%) & 2 (0.7\%) \\   \cline{2-5}
        & Some high school & 6 (1.6\%) & 3 (3.7\%) & 4 (1.4\%) \\ \cline{2-5}
        & High school grad & 39 (10.2\%) & 13 (15.9\%) & 22 (7.9\%) \\ \cline{2-5}
        & Some college & 100 (26.2\%) & 28 (34.1\%) & 60 (21.7\%) \\ \cline{2-5}
        & College grad & 95 (24.9\%) & 19 (23.2\%) & 75 (27.1\%) \\ \cline{2-5}
        & Grad/professional school & 126 (33.1\%) & 16 (19.5\%) & 106 (38.3\%) \\\hline\hline
    \end{tabular}
    \caption{\label{tab:demo}Subject demographics of the ECHO RESONANCE cohort.}
\end{table}
